---
title: "Introduction to R Markdown"
author: Mari Sanders 
date: 2024-09-10
output: 
  html_document: 
    toc: true
    toc_float: true
    code_folding: hide
---


```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```
Loaded necessary packages (e.g. `tidyverse`)

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Learning Assessment 
Creates a `test_frame` and plots a histogram
```{r la_chunk, message = FALSE} 

test_frame <- tibble(
  vec_numeric = rnorm(500, 1),
  vec_logical = vec_numeric > 0, 
  vec_abs = abs(vec_numeric)
)

ggplot(test_frame, aes(x = vec_abs)) + 
  geom_histogram()
```

# Formatting 

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_

**bold**  or  __bold__

`code`

superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell